A Spatial AR System for Axis-aligned Augmentation of Planar Scenes in Industrial Settings

### 2021-07-14 paper/elsarticle/elsarticle-template.tex
paper

Augmented reality (AR) \cite{van2010survey,zhou2008trends} promises to enable use cases in industrial settings that include the embedding of assembly instructions directly into the scene \cite{schlund2018moglichkeiten,masood2019augmented,gattullo2019towards}, potentially reducing or altogether doing away with the need for workers to refer to instructions in paper form or on a screen. Typically, AR works by embedding the augmentation in an image of the scene acquired from the viewpoint of a single individual, with the resulting augmented image in turn displayed using some form of head-mounted display. Reliance on head-mounted displays, however, has two adverse consequences: (i) a head-mounted display must be worn by each individual wishing to view the augmentation, and (ii) such a head-mounted display---in some cases taking the form of a helmet in order to house multiple sensors in support of accurately tracking the viewpoint of the viewer relative to the scene---can be obtrusive. \textit{Spatial} AR is a form of augmented reality carried out not by embedding the augmentation in an image of the scene as with head-mounted displays, but by projection to the scene itself \cite{bimber2019spatial}, thus eliminating both aforementioned problems. Yet considering for the moment a planar surface to be augmented, unless the projector faces the surface frontally, the bounds of a projected rectangular image will not appear rectangular; more generally, they will instead appear trapezoidal (i.e., the projected image will appear distorted). Such distortions can be eliminated by carrying out a cumbersome manual process called keystone correction to appropriately warp the image to be projected, often using software bundled with the projector.

@@

The hardware setup employed in the evaluation comprised a Panasonic PT-RZ660BE projector with a steerable mirror system---used in our experiments to point the projection to each of the 15 locations---manufactured by Dynamic Projection Institute \cite{rupprecht2020information}. The steerable mirror system was bundled with the MDC-X software for steering the mirror, loading imagery, and optionally carrying out manual keystone correction, such that each position and (warped) image can be registered as a preset. In addition, we used a downward-facing Zed 2 stereo camera manufactured by Stereolabs, yet relied only on the left view. The floorspace used for our experiments measured dimensions of ca.\ 6~m~$\times$~4~m; the projector was mounted at approximately the center of this space, at a height of ca.\ 3.5 m.

>>>>

Augmented reality (AR) \cite{van2010survey,zhou2008trends} promises to enable use cases in industrial settings that include the embedding of assembly instructions directly into the scene \cite{schlund2018moglichkeiten,masood2019augmented,gattullo2019towards,rupprecht2020information,Rupprecht2021}, potentially reducing or altogether doing away with the need for workers to refer to instructions in paper form or on a screen. Typically, AR works by embedding the augmentation in an image of the scene acquired from the viewpoint of a single individual, with the resulting augmented image in turn displayed using some form of head-mounted display. Reliance on head-mounted displays, however, has two adverse consequences: (i) a head-mounted display must be worn by each individual wishing to view the augmentation, and (ii) such a head-mounted display---in some cases taking the form of a helmet in order to house multiple sensors in support of accurately tracking the viewpoint of the viewer relative to the scene---can be obtrusive. \textit{Spatial} AR is a form of augmented reality carried out not by embedding the augmentation in an image of the scene as with head-mounted displays, but by projection to the scene itself \cite{bimber2019spatial}, thus eliminating both aforementioned problems. Yet considering for the moment a planar surface to be augmented, unless the projector faces the surface frontally, the bounds of a projected rectangular image will not appear rectangular; more generally, they will instead appear trapezoidal (i.e., the projected image will appear distorted). Such distortions can be eliminated by carrying out a cumbersome manual process called keystone correction to appropriately warp the image to be projected, often using software bundled with the projector.

@@

The hardware setup employed in the evaluation comprised a Panasonic PT-RZ660BE projector with a steerable mirror system---used in our experiments to point the projection to each of the 15 locations---manufactured by Dynamic Projection Institute \cite{rupprecht2020information,Rupprecht2021}. The steerable mirror system was bundled with the MDC-X software for steering the mirror, loading imagery, and optionally carrying out manual keystone correction, such that each position and (warped) image can be registered as a preset. In addition, we used a downward-facing Zed 2 stereo camera manufactured by Stereolabs, yet relied only on the left view. The floorspace used for our experiments measured dimensions of ca.\ 6~m~$\times$~4~m; the projector was mounted at approximately the center of this space, at a height of ca.\ 3.5 m.
